---
output: 
  github_document:
    df_print: tibble
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
requireNamespace("tibble", quietly = TRUE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swmm

<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/paleolimbot/swmm.svg?branch=master)](https://travis-ci.org/paleolimbot/swmm)
[![Codecov test coverage](https://codecov.io/gh/paleolimbot/swmm/branch/master/graph/badge.svg)](https://codecov.io/gh/paleolimbot/swmm?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of swmm is to provide a cross-platform interface to the [United States Environmental Protection Agency](https://www.epa.gov/)'s [Stormwater Management Model (SWMM)](https://www.epa.gov/water-research/storm-water-management-model-swmm) (the [source for SWMM is also available on GitHub](https://github.com/USEPA/Stormwater-Management-Model).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/swmm")
```

If you can load the package, you're all set! There is no need to install SWMM (the package contains a copy).

```{r}
library(swmm)
```

## Running SWMM

Run SWMM using the `swmm_run()` function and an ".inp" input file.

```{r run}
result <- swmm_run(swmm_example_file("Example8.inp"))
result
```

You can find out which version of SWMM is included in the package with `swmm_version()`:

```{r}
swmm_version()
```

## Reading swmm output

Use the `swmm_read_*()` functions (highly experimental):

```{r}
out_file <- result$out

swmm_read_subcatchments(out_file)
swmm_read_links(out_file)
swmm_read_nodes(out_file)
swmm_read_system(out_file)
```

To find out which variables there are to choose from (for the purposes of only reading part of the output, which you probably want to do), use `swmm_read_variables()`:

```{r}
swmm_read_variables(out_file)
```
